%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Hardware Engineer} % Job title
    {Dinamo Networks} % Organization
    {Brasília, Brazil} % Location
    {Apr. 2023 - TODAY} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mechanical and electronics design of Hardware Security Modules (HSMs).}
        \item {Worked alongside metallurgical companies to ensure product quality in the manufacturing of mechanical components.}
        \item {Developed and improved PCB layouts in various products, and created prototypes/proofs of concept using ARDUINO and Raspberry Pi.}
        \item {Involved in technical support, equipment assembly, and product certification in Brazil (INMETRO/ITI) and the USA (NIST) for compliance.}
        \item {All responsibilities i had as an intern as the sole responsible for the production department.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hardware Engineer Intern} % Job title
    {} % Organization
    {} % Location
    {Jul. 2021 - Mar. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {C/C++ programming/implementing of features in embedded systems, with Linux environment.}
        \item {Development of gigas for mechanical and electrical tests.}
        \item {Assist in the assembly, adaptation, and quality assurance of products on national and international standards.}
        \item {Stock management, virtual and physical, with ERP platform.}
        \item {Optimization and documentation of small production pipeline.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant, Developer, and Manager (VOLUNTEER)} % Job title
    {Mecajun - Junior Mechatronics} % Organization
    {Brasília, Brazil} % Location
    {Dez. 2019, DNov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance and development of a mobile in-pipe inspection vehicular robot.}
        \item {Mechanism, circuit, and PCB design for safe water pumping system for artistic presentations.}
        \item {Energy efficiency consulting for a nationally widely known fast food network.}
        \item {Organization, planning, and acquisition of human and financial resources in various different management strategies for engineering projects.}
        \item {Follow-up of customers through the sales funnel, assisting the project managers in direct contact with clients and partners.}
        \item {Demonstration of projects open to the public at universities, schools, and innovation-driven events.}
        \item {Negotiations, contract making and validation for the company, benchmarking, and partnership seeking.}
      \end{cvitems}
    }

\end{cventries}